Standartox: Standardising toxicity data

### 2020-04-06 article/article.tex
Updates from Overleaf

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
%% Additional packages
\usepackage{standalone}
% code
\usepackage{listings}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
% tikz
\usepackage{tikzpeople}
\usetikzlibrary{trees,
                arrows,
                shapes.geometric,
                positioning,
                calc,
                backgrounds,
                fit}
\usepackage{rotating}

@@

\begin{table}[H]
    \caption{R-packages used for the compilation of the Standartox database.}
    \label{tab:rpackages}
    \centering
\begin{tabular}{cc}
    \toprule
    \textbf{Title} & \textbf{Citation} \\ 
    \midrule
    devtools: Tools to Make Developing R Packages Easier & \citep{wickham_devtools_2019} \\
    RCurl: General Network HTTP FTP Client Interface for R & \citep{lang_rcurl_2020} \\
    stringr: Simple Consistent Wrappers for Common String Operations & \citep{wickham_stringr_2019} \\
    R: Various Programming Utilities & \citep{bengtsson_r_2019} \\
    udunits: Udunits 2 Bindings for R & \citep{hiebert_udunits_2016} \\
    rvest: Easily Harvest Scrape Web Pages & \citep{wickham_rvest_2019} \\
    httr: Tools for Working with URLs and HTTP & \citep{wickham_httr_2019} \\
    The: A Practical and Consistent Mapping Between JSON Data and R Objects & \citep{ooms_the_2014} \\
    readxl: Read Excel Files & \citep{wickham_readxl_2019} \\
    openxlsx: Read Write and Edit xlsx Files & \citep{schauberger_openxlsx_2019} \\
    purrr: Functional Programming Tools & \citep{henry_purrr_2019} \\ data: Extension of data frame & \citep{dowle_data_2019} \\
    RPostgreSQL: R Interface to the PostgreSQL Database System & \citep{conway_rpostgresql_2017} \\ DBI: R Database Interface & \citep{b_dbi_2019} \\
    vegan: Community Ecology Package & \citep{oksanen_vegan_2019} \\ The: NA & \citep{wickham_the_2011} \\
    outliers: Tests for outliers & \citep{komsta_outliers_2011} \\ feather: R Bindings to the Feather API & \citep{wickham_feather_2019} \\
    ggplot: Elegant Graphics for Data Analysis & \citep{wickham_ggplot_2016} \\ ggrepel: Automatically Position Non Overlapping Text Labels with & \citep{slowikowski_ggrepel_2019} \\
    ggridges: Ridgeline Plots in ggplot2 & \citep{wilke_ggridges_2018} \\
    scales: Scale Functions for Visualization & \citep{wickham_scales_2019} \\ treemapify: Draw Treemaps in ggplot2 & \citep{wilkins_treemapify_2019} \\ cowplot: Streamlined Plot Theme and Plot Annotations for ggplot2 & \citep{wilke_cowplot_2019} \\
    RColorBrewer: ColorBrewer Palettes & \citep{neuwirth_rcolorbrewer_2014} \\ treemap: Treemap Visualization & \citep{tennekes_treemap_2017} \\ rgbif: Interface to the Global Biodiversity Information Facility API & \citep{chamberlain_rgbif_2020} \\
    taxize: NA & \citep{chamberlain_taxize_2013} \\ countrycode: An R package to convert country names and country codes & \citep{bundock_countrycode_2018} \\ foreach: Provides Foreach Looping Construct for R & \citep{microsoft_foreach_2017} \\
    doParallel: Foreach Parallel Adaptor for the parallel Package & \citep{corporation_doparallel_2018} \\
    fst: Lightning Fast Serialization of Data Frames for R & \citep{klik_fst_2019} \\
    DT: A Wrapper of the JavaScript Library DataTables & \citep{xie_dt_2019} \\
    knitr: A General Purpose Package for Dynamic Report Generation in R & \citep{xie_knitr_2020} \\
    \bottomrule
\end{tabular}
\end{table}

@@

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{refs/references-standartox.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz
%% Additional packages
\usepackage{standalone}
% code
\usepackage{listings}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}
% tikz
\usepackage{tikzpeople}
\usetikzlibrary{trees,
                arrows,
                shapes.geometric,
                positioning,
                calc,
                backgrounds,
                fit}
\usepackage{rotating}
% check references
\usepackage{refcheck}

@@

\begin{table}[H]
    \caption{R-packages used for the compilation of the Standartox database.}
    \label{tab:rpackages}
    \centering
\begin{tabular}{cc}
\toprule
\textbf{Title} & \textbf{Citation} \\ 
\midrule
bib2df: Parse a BibTeX File to a Data Frame & \citep{R-bib2df} \\
countrycode: Convert Country Names and Country Codes & \citep{R-countrycode} \\
cowplot: Streamlined Plot Theme and Plot Annotations for 'ggplot2' & \citep{R-cowplot} \\
data.table: Extension of `data.frame` & \citep{R-data.table} \\
DBI: R Database Interface & \citep{R-DBI} \\
dbreport: Automated reports from tables & \citep{R-dbreport} \\
devtools: Tools to Make Developing R Packages Easier & \citep{R-devtools} \\
doParallel: Foreach Parallel Adaptor for the 'parallel' Package & \citep{R-doParallel} \\
DT: A Wrapper of the JavaScript Library 'DataTables' & \citep{R-DT} \\
foreach: Provides Foreach Looping Construct for R & \citep{R-foreach} \\
fst: Lightning Fast Serialization of Data Frames for R & \citep{R-fst} \\
ggplot2: Create Elegant Data Visualisations Using the Grammar of Graphics & \citep{R-ggplot2} \\ httr: Tools for Working with URLs and HTTP & \citep{R-httr} \\
jsonlite: A Robust, High Performance JSON Parser and Generator for R & \citep{R-jsonlite} \\
knitr: A General-Purpose Package for Dynamic Report Generation in R & \citep{R-knitr} \\
openxlsx: Read, Write and Edit xlsx Files & \citep{R-openxlsx} \\ plotly: Create Interactive Web Graphics via 'plotly.js' & \citep{R-plotly} \\ plumber: An API Generator for R & \citep{R-plumber} \\
R.utils: Various Programming Utilities & \citep{R-R.utils} \\
RColorBrewer: ColorBrewer Palettes & \citep{R-RColorBrewer} \\
reactlog: Reactivity Visualizer for 'shiny' & \citep{R-reactlog} \\
readxl: Read Excel Files & \citep{R-readxl} \\ rgbif: Interface to the Global 'Biodiversity' Information Facility API & \citep{R-rgbif} \\ RPostgreSQL: R Interface to the 'PostgreSQL' Database System & \citep{R-RPostgreSQL} \\ rvest: Easily Harvest (Scrape) Web Pages & \citep{R-rvest} \\ scales: Scale Functions for Visualization & \citep{R-scales} \\ shiny: Web Application Framework for R & \citep{R-shiny} \\ shinydashboard: Create Dashboards with 'Shiny' & \citep{R-shinydashboard} \\ shinydashboardPlus: Add More 'AdminLTE2' Components to 'shinydashboard' & \citep{R-shinydashboardPlus} \\ shinyjs: Easily Improve the User Experience of Your Shiny Apps in Seconds & \citep{R-shinyjs} \\ shinyWidgets: Custom Inputs Widgets for Shiny & \citep{R-shinyWidgets} \\ ssdtools: Species Sensitivity Distributions & \citep{R-ssdtools} \\ stringi: Character String Processing Facilities & \citep{R-stringi} \\ stringr: Simple, Consistent Wrappers for Common String Operations & \citep{R-stringr} \\ taxize: Taxonomic Information from Around the Web & \citep{R-taxize} \\ treemap: Treemap Visualization & \citep{R-treemap} \\ treemapify: Draw Treemaps in 'ggplot2' & \citep{R-treemapify} \\ udunits2: Udunits-2 Bindings for R & \citep{R-udunits2} \\ webchem: Chemical Information from the Web & \citep{R-webchem} \\ countrycode: An R package to convert country names and country codes & \citep{R-countrycode} \\ ggplot2: Elegant Graphics for Data Analysis & \citep{R-ggplot2} \\ The jsonlite Package: A Practical and Consistent Mapping Between JSON Data and R Objects & \citep{R-The jsonlite Package} \\ Dynamic Documents with {R} and knitr & \citep{R-Dynamic Documents with {R} and knitr} \\ knitr: A Comprehensive Tool for Reproducible Research in R & \citep{R-knitr} \\ plotly for R & \citep{R-plotly for R} \\ R Python, and Ruby clients for GBIF species occurrence data & \citep{R-R Python, and Ruby clients for GBIF species occurrence data} \\ R package stringi: Character string processing facilities & \citep{R-R package stringi} \\ taxize - taxonomic search and retrieval in R & \citep{R-taxize - taxonomic search and retrieval in R} \\ webchem:  retrieve chemical information from the web & \citep{R-webchem}
\\
\bottomrule
\end{tabular}
\end{table}

@@

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\nocite{*}
\externalbibliography{yes}
\bibliography{refs/references-standartox.bib,
              refs/references-standartox-rpackages.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
% \sampleavailability{Samples of the compounds ...... are available from the authors.}
